|

### 2022-12-13 r-report/Paper.tex
final

During the same period, China's emissions have risen rapidly. In 2004,
the country surpassed the U.S. as the world's largest greenhouse gas
emitter and is likely to retain that title for some time. In 2019, more
than 25\% of all global greenhouse gas emissions came from China, more
than the U.S. and (at the time still) EU-28 combined (see Figure 1). As
a consequence of this development, China's emissions profile changed
dramatically: While the agricultural sector still accounted for a large
share of emissions in the early 1970s, its contribution has been only
marginal in recent years. Figure 2 shows the large-scale
industrialization of the country starting in the mid-1990s and the
corresponding increase in emissions from the energy sector. More
recently, transport sector emissions have picked up speed, likely
reflecting the wealthy share of China's citizens spending more money on
individual (fossil-fuel based) modes of transport.

@@

Chinese carbon emissions growth was predominantly driven by its rapid
economic development, which in turn caused the energy sector to grow
too. Since the year 2000, China's GDP per capita has more than
quadrupled, while carbon emissions have more than tripled in the same
period (see Figure 3). However, the growth of emissions has slowed in
recent years, as energy intensity of GDP had started decreasing after
the year 2005 and also carbon intensity of energy peaked in 2010 and has
been slowly decreasing since. While for the first two decades of the
21st century carbon emissions growth rates were closely resembling the
growth rates of GDP per capita, since 2010 the two numbers have
decoupled. China's immense expansion of renewable energy sources over
the last years is likely an underlying driver of this trend, however, as
we have seen, Chinese annual emissions remain very high at 14.2 GtCO2e
in 2019.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{Figure 1: Relative Emissions of the Top- 5 Polluters}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Figure 2: Total Emissions, China by Sector - 1970-2019}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Figure 3: Kaya Identity China - 2000 - 2019}
\end{figure}

@@

Figure 4 displays China's and developing and developed countries' Kaya
identities according to the IPCC classification in the Sixth Assessment
Report from 2000 to 2019. In those years, China's GDP per capita was
growing with a factor close to five, thereby being the strongest upward
driver of emissions. GDP per capita increased almost in tandem with
carbon emissions until 2010, in which a decoupling took place. Ever
since, Chinese emission's growth rates have been much slower than those
of GDP per capita. This decoupling is likely due to the decreasing
energy intensity of GDP and carbon intensity of energy at the same time.
The energy intensity is the main counteracting factor on Chinese
emissions and decreased constantly since 2005. The decreasing trend
seemed to have already started in 2000 but had rebounded before 2005,
which can be traced back to 2001, when China joined the WTO
\citep{Zheng2020}. However, since 2010 the decrease has been
significant, hence driving the reduction of overall emissions growth
rate. Furthermore, one can see that carbon intensity of energy decreased
since 2010 meaning that the amount of CO2 per unit of energy is
decreasing. Nevertheless, the relationship remains a positive one. The
decline of both the energy intensity and carbon intensity is likely due
to economic efficiency improvements. Additionally, carbon intensity
further declined because of increasing capacity additions of renewable
energies (changes in the fossil share) and the reduced emission
intensity of fossil fuels (changes in the fossil intensity, fuel switch)
\citep{Zheng2020, Peters2017}. Population changes only played a minor
role but can be considered as a persistent upward driver of emissions.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Figure 4: Kaya Identities - 2000 - 2019\textbar{} China
vs.~Developed and Developing according to AR\_6 Classification}
\end{figure}

Thus, in the next steps, the World Bank's Income Classification Scheme
will be used for comparison (Figure 5). In high-income countries, GDP
per capita and population are increasing only at low levels (by roughly
the factor 0.5 and 0.2 respectively). Carbon intensity and energy
intensity are decreasing, keeping carbon emissions down. The carbon
intensity is decreasing because of two factors: the fossil intensity and
the fossil share. In contrast, in low-income countries, the growth of
CO2 emissions is exceeding the growth of GDP per capita, both rising by
a factor of 2.8 and 5 respectively over the observed time span. This is
driven by a high and increasing carbon intensity. Furthermore,
population growth plays an important role in this group, and can be
considered a further driving factor of CO2 emissions. The only
contrasting factor is the decreasing energy intensity. Comparing both
groups of countries to China, one can resume that China's development
does not fit in either of the groups perfectly. Like before China's Kaya
decomposition shares similar characteristics as both groups: The small
population growth resembles the trend of high-income countries, the
dramatically decreasing energy resembles the trend of low-income
countries. Considering lower-middle income countries, they seem to show
upwards trends in any of the indicators except for energy intensity. In
comparison, in upper-middle income countries carbon emissions and GDP
per capita develop in tandem, while carbon intensity and energy
intensity only fluctuate around zero in the years from 2000 to 2019.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Figure 5:Kaya Identities - 2000 - 2019\textbar{} China
vs.~Developed and Developing according to AR\_6 Classification}
\end{figure}

@@

In this part, sector trends of different groups of countries will be
considered using the same two categories of country groups as before. We
take into account five sectors: energy, industry, transport, AFOLU
(which in the EDGAR database only includes agricultural emissions), and
buildings. China's relative GHG emissions by sector are presented in a
stacked bar plot in Figure 6 \& 7. Most of China's emissions in 2019
came from the energy and industry sector with 44\% and 38\%
respectively. Only smaller shares are attributable to transport (6\%),
buildings (5\%) and AFOLU (6\%).

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Figure 6}
\end{figure}

As before, to get a more granular view on the split of emissions by
sector, the World Bank's classification will be consulted (Figure 7).

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{Figure 7}
\end{figure}

As the stacked bar plot can only provide a snapshot in time and relative
emissions only tell a limited story, we will in a next step compare
China's per capita emissions by sector over time from 1970 to 2019 to
those of our four income determined country groups (Figure 8).

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{Figure 8}
\end{figure}

@@

The resulting sectoral emissions pathways for each country/region are
depicted in figure xx. The resulting cumulative emissions forecasts for
the three countries/blocks are shown in figure xx. Accordingly, China
will pass the EU-27 in cumulative GHG emissions in 2027 and is projected
to pass the U.S. in 2032 . Afterwards it will be the largest cumulative
emitter.

These projections hold even when modelling each sector according to the
Chinese NDC (assuming peak years of 2030 and zero emissions by 2060). In
the NDC-scenario China will surpass the EU and US respectively in the
same years as modeled in our main scenarios, but at different emission
levels -- 452.4 GtCO2eq (main scenario) 451.8 GtCO2eq (NDC-scenario).
When projecting only CO2 emission developments1 China will surpass the
EU in 2031 and the US in 2038 according to both scenarios.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{Figure 9}
\end{figure}

@@

First, we consider China's responsibility based on absolute emissions in
the year 2019 (Figure X). In the ranking, China ranks on first place
with absolute emissions of 14,219.37 Mt CO2 eq. This is more than double
of the U.S. emissions (6,266.8 Mt CO2 eq) and also close to the
emissions of all other countries that do not belong to the group of the
top 10 emitters combined (14,075.12 Mt CO2 eq). Together with the U.S.,
India and Russia, China makes up for 50\% of global emissions, but these
four countries do not produce half of the global GDP, nor do they
represent half of the world's population. This highlights that the
responsibility of these four countries to drastically reduce emissions
is high. Considering that China is producing more than double the
emissions of the U.S., China has by far the highest responsibility to
mitigate climate change from a current absolute emissions perspective.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Figure 10: Absolute GHG Emission - 2019 \textbar{} Top
Emittters, China, US, EU-27 and reference for GDP, Emissions and
Population}
\end{figure}

Next, we consider emissions per capita (Figure x). This is important as
China is the country with the biggest population worldwide of approx.
1.4 billion people \citep{WorldBank2022c}. Looking at this ranking, it
is important to consider that the top emitters according to per capita
emissions are relatively small countries with low absolute emissions but
also small populations. Thus, when it comes to reducing absolute
emissions and fighting climate change, they can only play a minor role.
China interestingly ranks on place 43 with roughly 10t CO2 eq / capita,
before EU-27 but behind the U.S. (Ranking: 17). According to this equity
metric, China's fair share to mitigate climate change from this
perspective should be located between the share of these two
countries/groups of countries.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{Figure 11: Per Capita Emissions- 2019 \textbar{} Top Emittters,
China, US, EU-27 and reference for GDP, Emissions and Population}
\end{figure}

Considering GDP and GDP per capita refers to the capacity of acting on
climate change, following the assumption that richer countries have more
resources available to fight climate change. As Figure XX shows, China
had the highest GDP of all countries in 2019, with USD 22.49 trillion.
Based on this, China would theoretically have to make the greatest
conribution to reduce emissions. Absolute GDP, however, is limited in
telling us about a country's actual capacity because it ignores
population size. Therefore, considering GDP per capita might be more
worthwhile. Here China only ranks 81st place in the world. Therefore,
China's responsibility is relatively low from the GDP per capita
perspective. In comparison, the U.S. rank on place 11. Countries that
are in the top 10 emitters are often relatively small countries deriving
their wealth from natural resources. Hence, they have a high
responsibility to mitigate climate change as they have the ability to
pay for climate change mitigation measures. However, their absolute
emissions are relatively small and thus an ambitious reduction might not
make a huge difference for achieving climate targets. Thus, one should
consider that these countries should specifically contribute by
providing financial aid to mitigate emissions elsewhere.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{Figure 12: Absolute GDP p - 2019 \textbar{} Highes GDP
Countries, China, US, EU-27 and reference for GDP, Emissions and
Population}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{Figure 13: GDP per Capita - 2019 \textbar{} Highes GDP
Countries, China, US, EU-27 and reference for GDP, Emissions and
Population}
\end{figure}

>>>>

During the same period, China's emissions have risen rapidly. In 2004,
the country surpassed the U.S. as the world's largest greenhouse gas
emitter and is likely to retain that title for some time. In 2019, more
than 25\% of all global greenhouse gas emissions came from China, more
than the U.S. and (at the time still) EU-28 combined (see Figure 1.1).
As a consequence of this development, China's emissions profile changed
dramatically: While the agricultural sector still accounted for a large
share of emissions in the early 1970s, its contribution has been only
marginal in recent years. Figure 1.2 shows the large-scale
industrialization of the country starting in the mid-1990s and the
corresponding increase in emissions from the energy sector. More
recently, transport sector emissions have picked up speed, likely
reflecting the wealthy share of China's citizens spending more money on
individual (fossil-fuel based) modes of transport.

@@

Chinese carbon emissions growth was predominantly driven by its rapid
economic development, which in turn caused the energy sector to grow
too. Since the year 2000, China's GDP per capita has more than
quadrupled, while carbon emissions have more than tripled in the same
period (see Figure 1.3). However, the growth of emissions has slowed in
recent years, as energy intensity of GDP had started decreasing after
the year 2005 and also carbon intensity of energy peaked in 2010 and has
been slowly decreasing since. While for the first two decades of the
21st century carbon emissions growth rates were closely resembling the
growth rates of GDP per capita, since 2010 the two numbers have
decoupled. China's immense expansion of renewable energy sources over
the last years is likely an underlying driver of this trend, however, as
we have seen, Chinese annual emissions remain very high at 14.2 GtCO2e
in 2019.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{Relative Emissions of the Top-5 Polluters}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Total Emissions, China, by Sector, 1970-2019}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Kaya Identity, China, 2000-2019}
\end{figure}

@@

Figure 3.1 displays China's and developing and developed countries' Kaya
identities according to the IPCC classification in the Sixth Assessment
Report from 2000 to 2019. In those years, China's GDP per capita was
growing with a factor close to five, thereby being the strongest upward
driver of emissions. GDP per capita increased almost in tandem with
carbon emissions until 2010, in which a decoupling took place. Ever
since, Chinese emission's growth rates have been much slower than those
of GDP per capita. This decoupling is likely due to the decreasing
energy intensity of GDP and carbon intensity of energy at the same time.
The energy intensity is the main counteracting factor on Chinese
emissions and decreased constantly since 2005. The decreasing trend
seemed to have already started in 2000 but had rebounded before 2005,
which can be traced back to 2001, when China joined the WTO
\citep{Zheng2020}. However, since 2010 the decrease has been
significant, hence driving the reduction of overall emissions growth
rate. Furthermore, one can see that carbon intensity of energy decreased
since 2010 meaning that the amount of CO2 per unit of energy is
decreasing. Nevertheless, the relationship remains a positive one. The
decline of both the energy intensity and carbon intensity is likely due
to economic efficiency improvements. Additionally, carbon intensity
further declined because of increasing capacity additions of renewable
energies (changes in the fossil share) and the reduced emission
intensity of fossil fuels (changes in the fossil intensity, fuel switch)
\citep{Zheng2020, Peters2017}. Population changes only played a minor
role but can be considered as a persistent upward driver of emissions.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Kaya Identities, 2000-2019, China vs.~Developed/Developing
according to AR\_6 Classification}
\end{figure}

Thus, in the next steps, the World Bank's Income Classification Scheme
will be used for comparison (Figure 3.2). In high-income countries, GDP
per capita and population are increasing only at low levels (by roughly
the factor 0.5 and 0.2 respectively). Carbon intensity and energy
intensity are decreasing, keeping carbon emissions down. The carbon
intensity is decreasing because of two factors: the fossil intensity and
the fossil share. In contrast, in low-income countries, the growth of
CO2 emissions is exceeding the growth of GDP per capita, both rising by
a factor of 2.8 and 5 respectively over the observed time span. This is
driven by a high and increasing carbon intensity. Furthermore,
population growth plays an important role in this group, and can be
considered a further driving factor of CO2 emissions. The only
contrasting factor is the decreasing energy intensity. Comparing both
groups of countries to China, one can resume that China's development
does not fit in either of the groups perfectly. Like before China's Kaya
decomposition shares similar characteristics as both groups: The small
population growth resembles the trend of high-income countries, the
dramatically decreasing energy resembles the trend of low-income
countries. Considering lower-middle income countries, they seem to show
upwards trends in any of the indicators except for energy intensity. In
comparison, in upper-middle income countries carbon emissions and GDP
per capita develop in tandem, while carbon intensity and energy
intensity only fluctuate around zero in the years from 2000 to 2019.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Kaya Identities, 2000-2019, China vs.~Developed and Developing
according to AR\_6 Classification}
\end{figure}

@@

In this part, sector trends of different groups of countries will be
considered using the same two categories of country groups as before. We
take into account five sectors: energy, industry, transport, AFOLU
(which in the EDGAR database only includes agricultural emissions), and
buildings. China's relative GHG emissions by sector are presented in a
stacked bar plot in Figure 3.3 \& 3.4. Most of China's emissions in 2019
came from the energy and industry sector with 44\% and 38\%
respectively. Only smaller shares are attributable to transport (6\%),
buildings (5\%) and AFOLU (6\%).

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Relative Sector Emissions, 2019, China vs.~Developed/Developing
according to AR\_6 Classification}
\end{figure}

As before, to get a more granular view on the split of emissions by
sector, the World Bank's classification will be consulted (Figure 3.4).

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{Relative Sector Emissions, 2019, China vs.~Countries classified
by Income Levels}
\end{figure}

As the stacked bar plot can only provide a snapshot in time and relative
emissions only tell a limited story, we will in a next step compare
China's per capita emissions by sector over time from 1970 to 2019 to
those of our four income determined country groups (Figure 3.5).

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{Per Capita Emissions, by Sector, 1970-2019, China vs.~Countries
classified by Income Levels}
\end{figure}

@@

The resulting sectoral emissions pathways for each country/region are
depicted in Figure 3.6, with change rates being displayed in Figure 3.7.
The resulting cumulative emissions forecasts for the three
countries/blocks are shown in Figure 3.8. Accordingly, China will pass
the EU-27 in cumulative GHG emissions in 2027 and is projected to pass
the U.S. in 2032. Afterwards it will be the largest cumulative emitter.

These projections hold even when modelling each sector according to the
Chinese NDC (assuming peak years of 2030 and zero emissions by 2060, see
Figure 3.9 for comparison). In the NDC-scenario China will surpass the
EU and US respectively in the same years as modeled in our main
scenarios, but at different emission levels -- 452.4 GtCO2eq (main
scenario) 451.8 GtCO2eq (NDC-scenario). When projecting only CO2
emission developments1 China will surpass the EU in 2031 and the US in
2038 according to both scenarios.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{GHG Emissions Forecast, China vs.~EU vs.~US}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{GHG Emissions Forecast, China vs.~EU vs.~US}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{Projected Cumulative Emissions, China, NDC Scenario}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{Projected Cumulative Emissions, China, Main Scenario}
\end{figure}

@@

First, we consider China's responsibility based on absolute emissions in
the year 2019 (Figure 3.10). In the ranking, China ranks on first place
with absolute emissions of 14,219.37 Mt CO2 eq. This is more than double
of the U.S. emissions (6,266.8 Mt CO2 eq) and also close to the
emissions of all other countries that do not belong to the group of the
top 10 emitters combined (14,075.12 Mt CO2 eq). Together with the U.S.,
India and Russia, China makes up for 50\% of global emissions, but these
four countries do not produce half of the global GDP, nor do they
represent half of the world's population. This highlights that the
responsibility of these four countries to drastically reduce emissions
is high. Considering that China is producing more than double the
emissions of the U.S., China has by far the highest responsibility to
mitigate climate change from a current absolute emissions perspective.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{Absolute GHG Emissions, 2019, Top Emittters, China, US, EU-27
and reference for GDP, Emissions and Population}
\end{figure}

Next, we consider emissions per capita (Figure 3.11). This is important
as China is the country with the biggest population worldwide of approx.
1.4 billion people \citep{WorldBank2022c}. Looking at this ranking, it
is important to consider that the top emitters according to per capita
emissions are relatively small countries with low absolute emissions but
also small populations. Thus, when it comes to reducing absolute
emissions and fighting climate change, they can only play a minor role.
China interestingly ranks on place 43 with roughly 10t CO2 eq / capita,
before EU-27 but behind the U.S. (Ranking: 17). According to this equity
metric, China's fair share to mitigate climate change from this
perspective should be located between the share of these two
countries/groups of countries.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{Per Capita GHG Emissions, 2019, Top Emittters, China, US, EU-27
and reference for GDP, Emissions and Population}
\end{figure}

Considering GDP and GDP per capita refers to the capacity of acting on
climate change, following the assumption that richer countries have more
resources available to fight climate change. As Figure 3.12 shows, China
had the highest GDP of all countries in 2019, with USD 22.49 trillion.
Based on this, China would theoretically have to make the greatest
contribution to reduce emissions. Absolute GDP, however, is limited in
telling us about a country's actual capacity because it ignores
population size. Therefore, considering GDP per capita might be more
worthwhile. Here China only ranks 81st place in the world. Therefore,
China's responsibility is relatively low from the GDP per capita
perspective. In comparison, the U.S. rank on place 11. Countries that
are in the top 10 emitters are often relatively small countries deriving
their wealth from natural resources. Hence, they have a high
responsibility to mitigate climate change as they have the ability to
pay for climate change mitigation measures. However, their absolute
emissions are relatively small and thus an ambitious reduction might not
make a huge difference for achieving climate targets. Thus, one should
consider that these countries should specifically contribute by
providing financial aid to mitigate emissions elsewhere.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{Absolute GDP 2019, Countries with highest GDP, China, US, EU-27
and reference for GDP, Emissions and Population}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-16-1.pdf}
\caption{GDP per Capita 2019, Countries with highest GDP, China, US,
EU-27 and reference for GDP, Emissions and Population}
\end{figure}
